\TITLE

### 2023-06-19 paper/main.tex
-m

\section{Introduction}
\label{sec:introduction}
Diagnostic services such as paternity tests, doping tests, or venereal disease tests are performed at diagnostic centres that require clients to provide biological materials such as blood, urine, stool, or saliva. Unfortunately, to process transactions, clients are often forced to reveal their identities. Such a combination of personal data with biological materials exposes clients to significant privacy risks.

Other examples of sensitive services are, legal services, such as legal advice that may require disclosure of the history of financial transactions and confidential legal documents.

Banking services, such as credit scoring, may require sensitive personal data, such as medical records, and history of financial transactions.

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or accidentally (e.g., by theft) 
for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

Public individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.

The problem amplifies when personal information is linked to health records, or legal documents, or biological materials like DNA, saliva, or blood.

In such situations, customers may be reluctant to provide their personal information to the SP and thus resign from the service. Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients. Both parties are affected as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.

The guarantee of privacy of personal data is often based solely on trust in the SPs' staff and the security of their IT systems. However, we observe that personal data is often only used for logistical purposes, such as payments or communications, and could be provided anonymously if such methods were available.

It would be desirable for the customers to keep their identities private while still receiving the service. This could lead to reduced trust that customers have to put in SPs and less responsibility borne by SPs.

Examples of services that would benefit from the anonymity property are:
\begin{itemize}
    \item Patients willing to take a test eg.: for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private. Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.

Currently, they have to risk that their personal details, materials, and results are stored securely and kept private from any unauthorized actor (both curious employees and malicious attackers).

\item Individuals undertaking entrepreneurial activities may wish to obtain estimates of the risks and possible repercussions of the actions taken.

By exposing their identity they trust that the lawyer will not use that information for harmful actions.
\end{itemize}

In this work we explore the possibilities of providing services anonymously.

We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.

In our case, the customer who wants to use the service, exchanges his materials and money with the SP for the result of the service.

Our review indicates that none of the current systems is sufficient to achieve the desired goal. We propose a anonymous protocol for provisioning serivces that require physical materials. In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehavior of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item \textbf{Blockchain} (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain time without the trusted third party (TTP).
    \item \textbf{Anonymous payment methods}, like cash or anonymous cryptocurrencies, allowing customers to pay for services anonymously.
    \item \textbf{Decentralized storage network} (e.g., IPFS) to anonymously provide results together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.

    \item Cryptography:
    \begin{itemize}
        \item \textbf{Symmetric encryption}, to encrypt and decrypt results published on the public networks.
        \item \textbf{Diffie-Helman key exchange (DHKE)} to derive shared secrets for symmetric encryption.
        \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systematise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

The rest of this paper is organized as follows.
In Section~\ref{sec:related-works} we review related works. 
Then, in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, results availability, and anonymity.
Section~\ref{sec:protocol} provides detailed description of the protocol.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
Finally, Section~\ref{sec:conclusion} concludes the paper.

@@

\subsection{Fair exchange, physical delivery}
The most common application of fair exchange protocols is e-commerce. A typical transaction involves a seller and a buyer who exchange money for a physical product. To protect themselves the seller want to receive the funds prior to sending the product, while the buyer want to receive the product prior to paying. The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.

To our best knowledge, the first system that allowed for fair exchange of physical products was proposed by Zhang et al. in 2006~\cite{zhangPracticalFairExchangeEPayment2006}. The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity.

Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchange involving physical materials delivery. The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute. The protocol works as follows: 
\begin{enumerate}
\item The buyer sends an encrypted payment to the seller along with the proof of validity.
\item The seller validates the proof, which convinces him that the decrypted payment will also be valid.
\item The seller forwards the physical product to the trusted delivery agent (DA).
\item The buyer verifies whether the product is the one he ordered.
\item The buyer creates a proof of delivery and sends it along with the decryption key to the seller.
\end{enumerate}

However, the protocol relies on strong assumptions, namely, the existence of a TTP and an DA, who does not misbehave or collude with either party. Also the fairness is obtained assuming resilient communication channels.

@@

In the previous protocol, both parties of the transaction are known to each other. However, there are situations in which the buyer would prefer not to disclose his identity to the seller. The situation becomes more challenging when the transaction involves physical products.

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol involving physical products, which guarantees anonymity of both buyer and seller. They achieve it with the introduction of an online TTP that validates coins and guarantees fairness. Later, they proposed many extensions to the protocol, namely, in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend the anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries). Finally in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed improved protocol named PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).

Anonymity is ensured by using anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}. Fair exchange, physical delivery, and dispute resolution is achieved using delivery cabinet (DC) under the seller's control (e.g. Amazon Locker) and offline TTP that intervenes only in the case of a dispute.

The protocol works as follows:

\begin{enumerate}
    \item The buyer buys a digital coin from his bank. Blind signature is used to preserve privacy.
    \item The buyer sends to the seller the purchase details, address of DC, customer's bank signature, and some meta data to preserve the integrity of transaction, communication is done over Tor.
    \item The seller request a redemption of the digital coin.
    \item The seller posts the product to the DC via delivery serivice.
    \item The DA collects the product from the seller's cabinet and posts it to the DC.
    \item The buyer collects the product from the DC using a password.
    \item The buyer checks if the product is the ordered one, if not, opens a dispute to TTP.
\end{enumerate}

@@

\begin{itemize}
    \item the buyer's and seller's banks enable confidential transactions, and both share a commit buffer where the value is locked until the transaction is finished;
    \item banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item there exists an anonymous communication channel, and the SC and the DC protected by a passwords;
    \item the DC is equipped with a video camera that records the moment when the buyer opens the package and provides a way to submit the video to TTP in case of a dispute;
\end{itemize}

\subsection{Fair exchange and blockchain}

The issue of TTPs in fair exchange protocols has been solved by the usage of decentralized networks, especially blockchain technology.

The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it. As the service is widely used in the paper world, achieving it for e-mails has not yet met agreement across the scientific community. The main problem was the dependency on TTP, which significantly reduced the performance, security, and robustness of such protocols. The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.

Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.

The idea behind certified e-mails and any other fair exchange protocols is the following:
\begin{enumerate}
    \item The sender sends an encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.

In this case, the role of blockchain is to certify the existence of the decryption key at a certain time.

\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}

Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP. It provides an escrow service for the secure exchange of cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.

The protocol works as follows:
\begin{enumerate}
    \item Alice and Bob generate a 2-of-2 threshold escrow account using Thresh-Key-Gen protocol and send funds to it.
    \item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators that participate in the decentralized network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
    \item Alice and Bob encrypt each \textit{i}-th key share using public key of \textit{i}-th mediator.
    \item Alice and Bob exchange the sets of encrypted key shares with each other and send funds to the escrow account.
\end{enumerate}

The escrow is secure as long as \(t+1\) of mediators does not collude, which would let them recreate both \(x_A\) and \(x_B\).

To ensure that parties exchange actual key shares, they send witnesses generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.

In case of dispute, the decentralized network of mediators settles the conflict and grand one winning party the other party secret key, allowing it to withdraw the funds.

The monetary incentivization and reputation system guarantee the honesty of mediators.

@@

Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
physical delivery system. The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers. The whole route from a seller to a buyer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers. As long as the delivery providers do not collude, the seller neither can learn the identity nor destination address of the buyer.

A smart-contract is used to coordinate the whole process and mediate communication between the buyer and delivery providers.

However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.

@@

We considered only protocols that achieve fair exchange as it is the fundamental feature of such protocols.

Also, we didn't put much attention to the protocols for buying digital products as they are not relevant to our use case. The comprehensive analysis of such protocols is avaiable in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.

Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities. However, it does not provide dispute resolution.

Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain. However, it does not consider anonymity, disputes between parties nor physical material exchange.

Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowd-sourced dispute resolution system. However, it does not take anonymity into consideration.

Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coins' serial numbers.

Our protocol achieves anonymity by using either cash or privacy-preserving blockchains. Moreover, our protocol does not require a customer to submit any transaction to the message board, which in other protocols may be the weakest link in achieving the anonymity.

Moreover, none of them directly address our use case. We want the SP to remain public so that the anonymous buyer can easily start a dispute. We assume just one package of physical materials. Moreover, the package is delivered from the buyer to the SP, not the other way around — as it's the case for most e-commerce transactions.

Also, our protocol does not provide its own dispute-resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. 
It can be instantiated with either the local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

@@

The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature, but is based on strong or unpractical assumptions.

>>>>

\section{Introduction}
\label{sec:introduction}
Diagnostic services such as paternity tests, doping tests or venereal disease tests are carried out in diagnostic centres that require clients to provide biological material such as blood, urine, stool or saliva. Unfortunately, clients are often forced to reveal their identity in order to complete transactions. Such a combination of personal information with biological materials exposes clients to significant privacy risks.

Other examples of sensitive services include anonymous complaints or legal services, such as legal advice, which may require disclosure of financial transaction history and confidential legal documents. Banking services, such as credit scoring, may require sensitive personal information, such as medical records and financial transaction history.

Providing personal information exposes users to privacy risks, i.e. the potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or by accident (e.g. theft) for insider disclosure, unauthorised access or commercial gain. For example, by reselling it to marketers, financial institutions, other businesses, government agencies or even cybercriminals. 
This, in turn, can lead to unintentional GDPR or CCPA breaches, profiled advertising, or even criminal activity such as identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

Public figures such as influencers, politicians or celebrities are particularly vulnerable to this type of attack, as exposure of their health records, purchasing habits or legal documents can threaten their reputation, position or be used for blackmail.

The problem is compounded when personal information is linked to health records, legal documents or biological materials such as DNA, saliva or blood.
In such situations, clients may be reluctant to provide their personal information to the SP and therefore withdraw from the service. Both parties are harmed as the client does not receive a diagnosis relevant to their health and the SP loses potential clients.

The guarantee of privacy of personal data is often based solely on trust in the SP's staff and the security of their IT systems. However, we observe that personal data is often used only for logistical purposes, such as payment or communication, and could be provided anonymously if such methods were available.

It would be desirable for customers to keep their identity private while still receiving the service. This could lead to a reduction in the trust that customers need to place in SPs and a reduction in the responsibility that SPs bear.

Examples of services that would benefit from the anonymity property are:
\begin{itemize}
    \item Patients who are willing to take a test, e.g. for drugs, STDs, paternity or steroids, have a strong incentive to keep the whole process private. The mere fact that they have taken the test—without revealing the result—is suggestive enough to be used as a premise in the event of a conflict.

    Currently, they have to take the risk that their personal data, materials and results will be stored securely and kept secret from any unauthorised actor (both curious employees and malicious attackers).

\item Individuals engaged in entrepreneurial activities may want to assess the risks and possible consequences of their actions.

By revealing their identity, they trust that the lawyer will not use this information for harmful actions.
\end{itemize}

Using Solove's Taxonomy of Privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks:
\begin{itemize}
    \item \textbf{Breach of confidentiality}, breaking a promise to keep an individual's information confidential;
    \item \textbf{Disclosure}, revealing true information about a person that affects the way others judge their character;
    \item \textbf{Identification}, linking information to a specific individual;
    \item \textbf{Secondary use}, using personal information for a purpose other than that for which they were collected.
\end{itemize}

We consider the following adversaries:
\begin{itemize}
    \item \textbf{Malicious insiders}: Individuals or entities with authorised access to the protocol's systems or data who may abuse their privileges to compromise customer privacy. This could include employees, contractors or service providers;
    \item \textbf{Government agencies}: Depending on the jurisdiction and the nature of the protocol, government agencies may have legal powers or national security interests that could affect customer privacy. For example, the potential for surveillance, data requests or legal intervention;
    \item \textbf{Malicious third-party services}: If the protocol relies on third party services or APIs, the privacy of customer data could be at risk if these services have inadequate security measures in place or if they engage in data sharing or tracking without the consent of the customer;
    \item \textbf{Hackers and cybercriminals}: Individuals or organised groups with malicious intent who may exploit vulnerabilities in the protocol's implementation, infrastructure, or supporting systems to gain unauthorised access to customer information.
\end{itemize}

In this work we explore the possibilities of anonymous service provision and propose a protocol that preserves customer privacy even in the event of a successful attack. Under realistic operational assumptions, we believe that decoupling personal information from materials, payment and communication achieves a sufficient level of anonymity.

However, a protocol that hides a customer's identity is difficult to secure and coordinate. In particular, conflicts between customers and service providers are difficult to resolve when there is no one to accuse.

We observe that the problem of anonymous service provision can be seen as a problem of fair exchange, where parties exchange some goods fairly, i.e. either both parties obtain the goods, or they both obtain nothing.

In our case, the customer who wants to use the service exchanges his materials and money with the SP for the result of the service.

Our review shows that none of the current systems is sufficient to achieve the desired goal. We propose an anonymous protocol for the provision of services that require physical materials. In the event of a dispute, either due to missed deadlines or incorrect results, the customer can disclose the entire interaction, prove the SP's misbehaviour to justice, and win the dispute.

To achieve this goal we use
\begin{itemize}
    \item \textbf{Blockchain}, to achieve fairness, i.e. as a means of proving that certain actions took place at a certain time without the Trusted Third Party (TTP).
    \item \textbf{Anonymous payment methods}, such as cash or anonymous cryptocurrencies, which allow customers to pay for services anonymously.
\item \textbf{Decentralised storage network} (e.g. IPFS) to provide results together with a provable storage network (e.g. Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.

    \item Cryptography:
    \begin{itemize}
        \item \textbf{Symmetric encryption}, to encrypt and decrypt the results published on the public networks.
        \item \textbf{Diffie-Helman key exchange (DHKE)}, to derive shared secrets for symmetric encryption.
        \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

Figure~\ref{fig:protocol-overview} shows a simplified diagram of the protocol.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{protocol-overview.pdf}
\centering
\caption{A simplified diagram of the protocol. The first step involves the delivery of the materials to the SP. The second step involves anonymous payment. The third step involves the delivery of the results to the customer. Each step is proven on the message board, protecting the fair party in a conflict situation.}

\label{fig:protocol-overview}
\end{figure}

\paragraph{}
The contribution of our paper is:
\begin{itemize}
\item we propose a protocol that upon a realistic operational and threat model:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision involving \textbf{physical materials}, i.e., the service provider does not need to collect any personal information from the customer;
  \item achieves \textbf{fairness} by the use of blockchain and cryptographic proofs. We model the protocol as an interactive non-cooperative game and show fairness at each of its steps.
  \item \textbf{does not rely on a centralised TTP}, but uses a decentralised blockchain and a distributed content-addressable storage network;
  \item in conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user experience and practicality};
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item We implement a working prototype of the protocol and provide open source code.
\item We systematise often misused definitions of anonymity, pseudonymity, linkability and traceability.
\item We propose a framework for analysing fairness in fair exchange protocols and use it to prove the fairness of our protocol.
\item We discuss possible improvements to the protocol using secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

Some authors have proposed blockchain-based fair exchange systems that could be adapted to service provision; however, to the best of our knowledge, we are the first to propose a system that satisfies all of the above properties. In particular, anonymity and physical delivery have rarely been addressed together, and if so, the protocol was based on TTP and impractical assumptions about the banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

The rest of this paper is organised as follows.
In Section~\ref{sec:related-works} we review related works. 
Then in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, availability of results and anonymity.
Section~\ref{sec:protocol} provides a detailed description of the protocol.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:experiments} presents the implementation of the protocol and the results of our experiments.
Section~\ref{sec:discussion} discusses possible improvements in terms of crowdsourced dispute resolution or dispute avoidance, self-sovereign identities (SSIs), anonymous delivery, and formal verification.
Finally, Section~\ref{sec:conclusion} concludes the paper.

@@

\subsection{Fair exchange, physical delivery}
The most common application of fair exchange protocols is e-commerce. A typical transaction involves a seller and a buyer exchanging money for a physical product. To protect themselves, the seller wants to receive the funds before sending the product, while the buyer wants to receive the product before paying. The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.

To the best of our knowledge, the first system allowing fair exchange of physical products was proposed by Zhang et al. in 2006~\cite{zhangPracticalFairExchangeEPayment2006}. The protocol uses the buyer's bank as the TTP and assumes no coalition between the parties to achieve anonymity.

The authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed a protocol for fair exchange involving the delivery of physical materials. The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP which assumes the TTP is only involved in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP only gets involved in the event of a dispute. The protocol works as follows 
\begin{enumerate}
\item The buyer sends an encrypted payment to the seller along with proof of validity.
\item The seller validates the proof, which convinces him that the decrypted payment is also valid.
\item The seller forwards the physical product to the trusted Delivery Agent (DA).
\item The buyer verifies that the product is the one ordered.
\item The buyer creates a proof of delivery and sends it to the seller along with the decryption key.
\end{enumerate}

However, the protocol relies on strong assumptions, namely the existence of a TTP and a DA that do not misbehave or collude with either party. Fairness is also achieved by assuming resilient communication channels.

@@

In the previous protocol, both parties of the transaction are known to each other. However, there are situations in which the buyer would prefer not to disclose his identity to the seller. The situation becomes more challenging when the transaction involves physical products.
In the previous protocol, both parties to the transaction are known to each other. However, there are situations where the buyer would prefer not to reveal his identity to the seller. The situation becomes more difficult when the transaction involves physical products.

The authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for physical products that guarantees the anonymity of both buyer and seller. They achieve this by introducing an online TTP that validates coins and guarantees fairness. Later they proposed many extensions to the protocol, namely in~\cite{birjoveanuPreservingAnonymityFair2018} they proposed an anonymous e-commerce protocol that governs complex transactions, in~\cite{birjoveanuAnonymityComplexTransactions2019} they extend anonymity for both buyers and sellers (in our case SPs), and in~\cite{birjoveanuFairExchangeECommerce2020} they proposed a protocol that supports chained transactions (involving multiple active intermediaries). Finally, in~\cite{birjoveanuTwoPartyECommerceProtocols2022} they proposed an improved protocol called PPPDCP (Protocol with Physical Product Delivery Providing Customer's Privacy).

Anonymity is ensured by using an anonymous communication channel over Tor~\cite{dingledineTorSecondGenerationOnion2004} and blind signatures~\cite{chaumSecurityIdentificationTransaction1985}. Fair exchange, physical delivery and dispute resolution are achieved using a Delivery Cabinet (DC) under the control of the seller (e.g. Amazon Locker) and an offline TTP that only intervenes in the event of a dispute.

The protocol works as follows

\begin{enumerate}
    \item The buyer buys a digital coin from their bank. A blind signature is used to ensure privacy.
    \item The buyer sends the seller the purchase details, the address of the DC, the signature of the customer's bank and some metadata to preserve the integrity of the transaction, communication is done over Tor.
    \item The seller requests redemption of the digital coin.
    \item The seller posts the product to the DC via the delivery service.
    \item The Delivery Agent (DA) collects the product from the seller's locker and posts it to the DC.
    \item The buyer collects the product from the DC using a password.
    \item The buyer verifies that the product is the one ordered, if not, opens a dispute with TTP.
\end{enumerate}

@@

\begin{itemize}
    \item The buyer's and seller's banks allow confidential transactions, and both share a commit buffer where the value is locked until the transaction is complete;
    \item The banks maintain a global list of coin serial numbers to prevent problems with double spending;
    \item there is an anonymous communication channel and the SC and DC are password protected;
    \item The DC is equipped with a video camera that records the moment the buyer opens the package and provides a means to submit the video to TTP in the event of a dispute;
\end{itemize}

\subsection{Fair exchange and blockchain}
The problem of TTPs in fair exchange protocols has been solved by the use of decentralised networks, in particular blockchain technology.

The simplest example of a blockchain-based fair exchange protocol is the certified email protocol, where neither the sender can deny sending the email nor the recipient can deny receiving it. As this service is widely used in the paper world, achieving it for emails has not yet been agreed upon by the scientific community. The main problem has been the reliance on TTP, which significantly reduces the performance, security and robustness of such protocols. The protocols that do not use TTP suffer from high computational and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.

The authors of ~\cite{hinarejosSolutionSecureCertified2019} have replaced TTP with blockchain (specifically the bitcoin blockchain as a reference implementation), which acts as a secure, verifiable and decentralised TTP.

The idea behind certified email and any other fair exchange protocol is as follows:
\begin{enumerate}
    \item The sender sends an encrypted and signed message to the recipient.
    \item The recipient returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publishes the proof of delivery and the decryption key on a blockchain (or TTP in general).
    \item The recipient decrypts the encrypted message using the published decryption key.
\end{enumerate}

The non-repudiation requirement is achieved by the receiver sending the proof of delivery before having access to the decrypted message, and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP), so that the receiver cannot deny having received the message or having access to the decryption key—because it is publicly available.

In this case, the role of the blockchain is to certify the existence of the decryption key at a given point in time.

\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}
Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP. It provides an escrow service for the secure exchange of cryptocurrencies and digital goods. It also provides a decentralised dispute resolution system for resolving conflicts.

The protocol works as follows:
\begin{enumerate}
    \item Alice and Bob create a 2-of-2 threshold escrow account using the Thresh-Key-Gen protocol and send funds to it.
\item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators participating in the decentralised network and \(t+1\) is the threshold for a sufficient number of mediators to reconstruct the secret key.
    \item Alice and Bob encrypt each \textit{i}-th key share with the public key of \textit{i}-th mediator.
\item Alice and Bob exchange the sets of encrypted key shares and send funds to the escrow account.
\end{enumerate}

The escrow is secure as long as \(t+1\) of the mediators do not collude, which would allow them to reconstruct both \(x_A\) and \(x_B\).

To ensure that the parties exchange real key shares, they send witnesses generated using the Feldman VSS scheme and zero-knowledge proofs to guarantee consistency between witnesses and key shares.

In the event of a dispute, the decentralised network of mediators resolves the conflict and grants the winning party the other party's secret key, allowing it to withdraw the funds.

The financial incentives and the reputation system guarantee the honesty of the mediators.

@@

Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous physical delivery system. The protocol achieves anonymity by using onion routing (similar to the Tor network) to connect physical delivery providers. The entire path from a seller to a buyer is divided into multiple steps, and each step is performed by randomly selected delivery providers. As long as the couriers do not collude, the seller cannot learn the identity or destination address of the buyer.

A smart contract is used to coordinate the whole process and mediate communication between the buyer and the delivery providers.

However, because the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.

@@

We only considered protocols that achieve fair exchange, as this is the fundamental feature of such protocols.

We also didn't focus on protocols for buying digital products, as they are not relevant to our use case. A more comprehensive analysis of such protocols is available in~\cite{birjoveanuTwoPartyECommerceProtocols2022}.

Altawy et al. 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that provides anonymous physical delivery using onion routing and anonymous blockchain interaction, assuming unlinkability between pseudonyms and real identities. However, it does not provide dispute resolution.

Hinarejos et al. 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain. However, it does not take into account anonymity, disputes between parties, or the exchange of physical material.

Meng et al. 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol through the crowd-sourced dispute resolution system. However, it does not take anonymity into account.

Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, but it is based on strong assumptions, namely the existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coin serial numbers.

Our protocol achieves anonymity by using either cash or privacy-preserving blockchains. In addition, our protocol does not require a customer to submit a transaction to the bulletin board, which may be the weakest link in achieving anonymity in other protocols.

Furthermore, none of them directly address our use case. We want the SP to remain public so that the anonymous buyer can easily start a dispute. We assume a single package of physical materials. Also, the package is delivered from the buyer to the SP, not the other way around–as in most e-commerce transactions.

Also, our protocol does not have its own dispute resolution mechanism, as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. 
This can be instantiated either with the local court or police, or with one of the blockchain's
dispute resolution services such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

@@

The notation \textit{Pseudonymity} means that the anonymity is based on the assumption that the pseudonym is not linked to the real identity; \textit{TTP} means that the protocol uses a trusted third party; \textit{BC} means that the protocol uses a public blockchain; \textit{YES*} means that the protocol provides the feature but is based on strong or impractical assumptions.
